Lens Modeling in \sw

### 2014-01-18 text/ms.tex
Another edit of the Abstract.

\begin{abstract}
In Spacewarps, volunteers are invited to search the CFHTLS sky survey for
gravitational lens candidates.  Here we report on a web interface    \todo[red]{or should that be application?} that allows experienced
volunteers to model lens candidates found within the classification phase of the project. A sample of 29 simulated lenses
were modeled multiple times by different users.  The quality of the models were then
examined in several ways.  Particular attention was paid to the following: (i)~the image parities and
time arrivals were identified correctly in most cases, but not
always; (ii)~the mean convergence (equivalent to the enclosed mass)
was quite well constrained in the image region; (iii)~the performance
of experienced volunteers was comparable to professionals.
\end{abstract}

@@

xxx
Our present picture of the formation of the largest structures in the
Universe --- galaxies and clusters of galaxies --- is that
gravitational instabilities (whose early stages are observable as
fluctuations of the microwave background) caused a collapse into
gravitationally bound structures.  Dark matter would have dominated
the initial collapse, but once deep wells in the gravitational
potential appeared, gas would have fallen into them while radiating
away its gravitational potential energy through atomic processes to
form the first stars and galaxies.  With time, galaxies and clusters
would continue to merge and change their form.  This rough outline is
well-established now, but many puzzles remain to be solved before our
understanding is satisfactory.  To progress towards solving these, we
need more knowledge of dark matter.  And to study dark matter,
gravitational lensing is attractive, because it depends only on mass.

>>>>

\begin{abstract}
In the initial phase of Spacewarps (SW1), volunteers were invited to search the CFHTLS sky survey to look for gravitational lenses. Here we report on a web interface    
that gives experienced volunteers the opportunity to model the candidates that have been identified. These volunteers, were also invited to model a sample of 29 simulated lenses, to order to gauge the quality of the models that were being generated. These were then examined in greater detail, with particular attention being paid to the following: (i)~identification of image parities and time arrivals; (ii)~the mean convergence (equivalent to the enclosed mass), and finally;
 (iii)~ the performance of a volunteer vs. a professional. In most cases, the volunteers were found to correctly identify the image parities and time arrivals, along with a mean convergence that was contained within the image region; In all, the results could be comparable to that of professionals.

\todo[red]{or should that be web application? Also, I change the tense of the opening statement. Not too sure of the correct way of introducing an abbreviation (SW1 in this case), and I was a bit liberal with my editing - Sorry. Another comment - is 'Well contained' better than 'contained' or is it just a figure of speech?}

\end{abstract}

@@

Our present picture of the formation of the largest structures in the
Universe --- galaxies and clusters of galaxies --- is that
gravitational instabilities (whose early stages are observable as
fluctuations of the microwave background) caused a collapse into
gravitationally bound structures.  Dark matter would have dominated
the initial collapse, but once deep wells in the gravitational
potential appeared, gas would have fallen into them while radiating
away its gravitational potential energy through atomic processes to
form the first stars and galaxies.  With time, galaxies and clusters
would continue to merge and change their form.  This rough outline is
well-established now, but many puzzles remain to be solved before our
understanding is satisfactory.  To progress towards solving these, we
need more knowledge of dark matter.  And to study dark matter,
gravitational lensing is attractive, because it depends only on mass.
